Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-16 doc/paper.Rmd
commenting out section :: profile-summary.csv file missing

profc20 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:30-c:20.rds")
profc20$coarseness <- 0.2
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:30-c:25.rds")
profc30 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo:160-wv:30.rds")
profc30$coarseness <- .30
profc <- bind_rows(profc20, profc25, profc30)
profc <- profc %>% mutate(
  locations = chumbley %>% purrr::map_int(.f = function(x) {
    res <- NULL
    try(res <- x$locations[1], silent = TRUE)
    res
  })
)
profsumm <- read.csv("../data/profiles-summary.csv")
profsumm <- profsumm %>% select(-run_id)
profc <- profc %>% left_join(profsumm, by=c("land2_id"="land_id", "profile2_id"="profile_id"))

p2 <- profc %>% 
  ggplot(aes(x = locations/(length-wo))) +
  geom_histogram(binwidth = 0.025) +
  facet_grid(.~coarseness, labeller="label_both") + 
  theme_bw()

grid.arrange(p1, p2, ncol=1)
```

@@

\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
optimization && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_o$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

profc20 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_20.rds")
profc20$coarseness <- 0.2
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_25.rds")
profc30 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30.rds")
profc30$coarseness <- .30
profc <- bind_rows(profc20, profc25, profc30)
profc <- profc %>% mutate(
  locations = chumbley %>% purrr::map_int(.f = function(x) {
    res <- NULL
    try(res <- x$locations[1], silent = TRUE)
    res
  })
)
# profsumm <- read.csv("../data/profiles-summary.csv")
# profsumm <- profsumm %>% select(-run_id)
# profc <- profc %>% left_join(profsumm, by=c("land2_id"="land_id", "profile2_id"="profile_id"))
# 
# p2 <- profc %>% 
#   ggplot(aes(x = locations/(length-wo))) +
#   geom_histogram(binwidth = 0.025) +
#   facet_grid(.~coarseness, labeller="label_both") + 
#   theme_bw()
#  
# grid.arrange(p1, p2, ncol=1)
```

@@

\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
validation && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_v$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}
